Rigid fluid coupling

### 2022-03-08 manuscript/paper.tex
1st result, Mohseni sliding slope 2d done

@@

\subsection{Bouncing cube on a wall under gravity}
\label{sec:bouncing-cube}

\subsection{A test to check the conservation properties of rigid body}
\label{sec:conservation-of-rb-properties}

\subsection{Debris dam break flow}
\label{sec:debris-dam-break-canelas}

\subsubsection{Case I}
\label{sec:debris-dam-break-canelas-case-I}

\subsubsection{Case II}
\label{sec:debris-dam-break-canelas-case-II}

\subsubsection{Case III}
\label{sec:debris-dam-break-canelas-case-III}

\subsection{Dam break with body transport}
\label{sec:dam-break-with-body-transport}

\citet{wang2019numerical}

\subsection{Dam break with multiple bodies transport}
\label{sec:dam-break-with-multiple-bodies-transport}
\citet{wang2019numerical}

\subsection{Cylinders in water collapsed under gravity}
\label{sec:cylinders-collapse-in-water}
\citet{chen2019coupled}

>>>>

\subsection{3D Bouncing cube on a wall under gravity}
\label{sec:bouncing-cube}

\subsubsection{A test to check the conservation properties of rigid body}
\label{sec:conservation-of-rb-properties}

\subsection{Controlled Sliding on a Flat Surface}
\label{sec:controlled-rigid-body-sliding}

@@

\subsection{3D dam breaking flow hitting one cube}
\label{sec:3d-dam-breaking-one-cube-hit}

\cite{amaro2019improvement}

\subsection{3D dam breaking flow hitting three cube}
\label{sec:3d-dam-breaking-one-cube-hit}

\cite{amaro2019improvement}

\subsection{3D dam breaking flow hitting pyramid cubes configuration}
\label{sec:3d-dam-breaking-one-cube-hit}

\cite{amaro2019improvement}

% \subsection{Dam break with body transport}
% \label{sec:dam-break-with-body-transport}

% \citet{wang2019numerical}

% \subsection{Dam break with multiple bodies transport}
% \label{sec:dam-break-with-multiple-bodies-transport}
% \citet{wang2019numerical}

% \subsection{Cylinders in water collapsed under gravity}
% \label{sec:cylinders-collapse-in-water}
% \citet{chen2019coupled}
